Heavy inextensible strings in the Schwarzschild geometry

### 2024-11-01 weighted_string.Rmd
more work

```
EulerEquations[ 
  Sqrt[r[\[Phi]]^2 + 
     r'[\[Phi]]^2/(1 - 2*M/r[\[Phi]])]*(1 + \[Lambda]*(1 - 
        Sqrt[1 - 2*M/r[\[Phi]]])), r[\[Phi]], \[Phi]] // FullSimplify
```

Now define the  second derivative from Euler's equation:

```{r definerdashdash}
rdashdash <- function(r,rdash,lambda,M=1/2){
    x <- sqrt(1-2*M/r)
    return(
    (M*(4+lambda*(4-3*x))*r^2 + (-1+lambda*(-1+x))*r^3 + M*(3 + lambda*(3-2*x))*rdash^2 +
     2*r*(M^2*(-2+lambda*(-2+x)) + (-1+lambda*(-1+x))*rdash^2))/((-1+lambda*(-1+x))*r*(-2*M+r))
    )
}
```

@@

f <- approxfun(
    c(0,-0.1,-0.2,-0.5, -0.7, -1,  -1.4,     -1.6,-1.7),
    c(2.4,2.4, 2.1,1.5,   1.5, 0.5,  0.63, 0.3,0)
)

>>>>

Mathematica can deal with this.  The idiom is:

```
Needs["VariationalMethods`"]
EulerEquations[ 
  Sqrt[r[\[Phi]]^2 + 
     r'[\[Phi]]^2/(1 - 2*M/r[\[Phi]])]*(1 + \[Lambda]*(1 - 
        Sqrt[1 - 2*M/r[\[Phi]]])), r[\[Phi]], \[Phi]] // FullSimplify
```

The above comments give a second-order ODE, which is analytically
intractable.  However, we can proceeed by

```
Solve[%, r''[phi]] // FullSimplify
```

which gives an expression for $r''(\phi)$.  In R idiom, this is:

```{r definerdashdash}
rdashdash <- function(r,rdash,lambda,M=1/2){
    x <- sqrt(1-2*M/r)
    return(
    (
        M*(4+lambda*(4-3*x))*r^2 +
        (-1+lambda*(-1+x))*r^3 +
        M*(3 + lambda*(3-2*x))*rdash^2 +
        2*r*(M^2*(-2+lambda*(-2+x)) + (-1+lambda*(-1+x))*rdash^2)
    ) / (
        (-1+lambda*(-1+x))*r*(-2*M+r)
    )
    )
}
```

@@

f <- approxfun(
    c(0,-0.1,-0.2,-0.5, -0.7, -1,  -1.4,     -1.6,-1.7),
    c(2.4,2.4, 2.1,1.5,   1.5, 0.9,  0.63, 0.3,0)
)
